Distributions

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Labels for Figure 2.

# Fits

@@

```{r fig.width=12, fig.height=6}

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist)) -> pooling.support

@@

bar_col <- plot_grid(pooling.support + theme(legend.position = "none"),
                     pp.support, 
                     np.support + theme(legend.position = "none"),
                     ncol = 3, rel_widths = c(0.4, 1, 1.4))
plot_grid(bar_col, model.legend, nrow = 2, rel_heights = c(1, 0.1))

>>>>

<!-- # Fits  -->

@@

```{r Figure2, fig.width=12, fig.height=6}

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist)) -> pooling.support

@@

bar_col <- plot_grid(pooling.support + theme(legend.position = "none"),
                     pp.support, 
                     np.support + theme(legend.position = "none"),
                     ncol = 3, rel_widths = c(0.4, 1, 1.4), 
                     labels = c("A)", "B)", "C)"), label_size = 10)
plot_grid(bar_col, model.legend, nrow = 2, rel_heights = c(1, 0.1))

ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
